---
title: "Google Search crawling, HTTP status checks, URL snowballing, and text mining"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 

The following procedure has been developed to provide a stable URL collection method than can be coupled with text extraction and text burning features. The workflow has the flowwoing structure

```
[[GOOGLE SEARCH CRAWLING]]
_ create Google Search URLs
  |_ extract top hits from n pages
    x .. [[HTTP STATUS CHECKS]]
    |_ check whether the webpages are still available
      |_ y: keep
        x .. [[URL SNOWBALLING]]
        |_ for ervery google hit; SET: 
          |_ URL restriction parameter 
            [keywords that have to be in the URL for it to be added to the collection]
          |_ time limit for QUERY
            [from root URL]
        |_ for ervery google hit; DO.CALL: snowballing algorithm
            |_ access root URL; extract all hrefs
            |_ add hrefs to LOG-file{ONLY IF: new}
              |_ access new hrefs from LOG; extract all hrefs
              |_ add hrefs to LOG-file{ONLY IF: new}
                |_ .. UNTIL no new unique hrefs
                    .. BREAK{IF: time reached before collection completed}
                      [prevents endless crawling]
                      x .. [[HTTP STATUS CHECKS]]
                      |_ check whether the webpages are still available
                        |_ y: keep
                          ///// OPTIONAL: .. [[TEXT MINING]]
                          x
                          |_ exctract texts; SET:
                            |_ HTML elements that should be extracted
                            |_ preprocessing regex
                            |_ merged (y/n) [single/multielement]
                              x
                              |_ burning algorithm; SET:
                                ///// for EXPL see below
                                |_ buzzwords
                                |_ min.words
                                |_ min.avg.characters
                                |_ max.buzzwords
                                |_ sclicing
                                |_ slicing.keywords
                                |_ scnd.step.slicing
                                |_ scnd.step.threshold
                        |_ n: drop 
      |_ n: drop 
```

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
